\par{
I am a Principal Test Architect with over 13 years of comprehensive software quality engineering experience across enterprise, fintech, and cloud-native applications. I hold a Bachelor's degree in Computer Science (Trinity College Dublin), a Master's degree in Software Quality Engineering (University of Limerick), and advanced certifications in test automation and quality assurance.

Currently, I lead the Quality Engineering division at TechVision, where I architect enterprise-wide testing frameworks and establish quality standards across multiple product lines. I have pioneered automation-first strategies that reduced testing cycles by 60\% and led cross-functional teams in implementing continuous quality practices.

Throughout my career, I have driven transformational quality initiatives at leading organizations including CloudSync, DataFlow, and NetCorp. I specialize in test automation architecture, API and microservices testing, performance engineering, and E2E testing using Selenium, Robot Framework, and Java. I have deep expertise in building scalable test frameworks, CI/CD integration, contract testing, and continuous integration practices.

I am highly proficient with industry-standard tools including Selenium, TestNG, Robot Framework, Jenkins, GitLab CI, SonarQube, and have worked extensively with Java, Python, JavaScript, and Go. I am passionate about establishing quality culture, mentoring engineering teams, and implementing data-driven quality metrics.
}
\vspace{1em}