%Section: Professional Experience
\sectionTitle{Professional Experience}{\faSuitcase}
\vspace{1em}
\begin{experiences}
  \experience
    {Currently}{TechVision | Principal Test Architect, Quality Engineering Division}{Dublin}{IRELAND} {August 2024} {
           \begin{itemize}
               \item Architecting enterprise-wide test automation frameworks serving 8+ product lines.
               \item Leading quality transformation initiatives achieving 60\% reduction in testing cycle times.
               \item Establishing quality standards, test strategies, and continuous integration practices across organization.
               \item Mentoring and developing team of 12 QA engineers in advanced automation patterns and best practices.
               \item Implementing performance testing and load testing frameworks using JMeter and custom tools.
               \item Defining metrics-driven quality models and test coverage strategies aligned with business objectives.
           \end{itemize}
        }
        {JAVA, SELENIUM, ROBOT FRAMEWORK, TESTNG, JENKINS, GITLAB CI, JIRA, PERFORMANCE TESTING, MENTORING}
  \emptySeparator
  \experience
    {August 2024}{CloudSync Inc. | Principal Quality Engineer, Enterprise Platform}{London}{UK} {March 2022} {
           \begin{itemize}
               \item Led quality engineering for fintech platform processing 2M+ daily transactions.
               \item Designed and implemented comprehensive test automation framework using Selenium and TestNG.
               \item Established contract testing strategy achieving 95\% API coverage with Pact framework.
               \item Mentored team of 6 QA engineers and drove adoption of BDD practices enterprise-wide.
               \item Implemented performance testing and load simulation infrastructure using JMeter, reducing production incidents by 40\%.
               \item Developed and maintained CI/CD pipelines using Jenkins and GitLab, integrating quality gates.
           \end{itemize}
        }
        {JAVA, SELENIUM, TESTNG, PACT, JMETER, JENKINS, GITLAB CI, POSTGRESQL, MICROSERVICES, BDD}
  \emptySeparator
  \experience
    {March 2022}{DataFlow Systems | Senior QA Automation Engineer}{Amsterdam}{NETHERLANDS} {September 2019} {
           \begin{itemize}
               \item Designed and developed Robot Framework-based automation suite for data pipeline validation.
               \item Built REST API testing framework using Rest Assured and Cucumber for microservices testing.
               \item Implemented contract testing to ensure API compatibility across teams.
               \item Established automated test data generation using Python and custom ETL scripts.
               \item Optimized test execution reducing regression testing time from 4 hours to 30 minutes.
               \item Collaborated with development teams on test-driven development practices and ATDD methodologies.
           \end{itemize}
        }
        {ROBOT FRAMEWORK, REST ASSURED, PYTHON, CUCUMBER, JIRA, GIT, POSTGRESQL, API TESTING, ATDD}
  \emptySeparator
  \experience
    {September 2019}{NetCorp Solutions | Senior QA Engineer, Core Platform}{Toronto}{CANADA} {June 2017} {
            \begin{itemize}
                \item Developed comprehensive test automation strategy for enterprise B2B platform serving 5000+ customers.
                \item Implemented Selenium-based test framework with Java and Cucumber for cross-browser testing.
                \item Established performance testing baseline and identified bottlenecks using JMeter.
                \item Created and maintained test data management system using Python scripts and SQL.
                \item Reduced manual testing effort by 70\% through intelligent test automation.
                \item Coordinated with product and development teams on quality metrics and test coverage analysis.
            \end{itemize}
        }
        {JAVA, SELENIUM, CUCUMBER, JMETER, PYTHON, SQL, JIRA, CONFLUENCE, MANUAL TESTING, TEST STRATEGY}
  \emptySeparator
  \experience
    {June 2017}{Primacy Solutions | QA Automation Engineer, ERP Division}{Copenhagen}{DENMARK}
    {October 2015} {
            \begin{itemize}
                \item Developed automated test suites using Java and Selenium for ERP systems serving enterprise clients.
                \item Implemented Cucumber-based BDD framework improving collaboration between QA and business teams.
                \item Created and executed test plans for functional and regression testing across multiple modules.
                \item Performed API testing using REST clients and custom automation scripts.
                \item Provided technical leadership on testing best practices and quality standards.
                \item Integrated automated tests into CI/CD pipeline using Jenkins.
            \end{itemize}
        }
        {JAVA, SELENIUM, CUCUMBER, REST APIS, JIRA, CONFLUENCE, JENKINS, POSTGRESQL, AGILE}
  \emptySeparator
  \experience
    {October 2015} {TechVision Labs | QA Analyst, Quality Assurance}{Barcelona}{SPAIN}
    {August 2013}    {
              \begin{itemize}
                \item QA Analyst for e-commerce platform supporting 50+ market regions.
                \item Executed manual and automated functional test cases across web and mobile interfaces.
                \item Created test documentation and maintained test case repository.
                \item Performed localization and internationalization testing in 15 languages.
                \item Analyzed test results and documented defects for developer resolution.
                \item Collaborated with product teams to understand requirements and define test scenarios.
              \end{itemize}
        }
        {SELENIUM, JIRA, CONFLUENCE, MANUAL TESTING, TEST DOCUMENTATION, JAVA, RESPONSIVE DESIGN}
  \emptySeparator
  \experience
    {August 2013}     {Innovation Tech Hub | Quality Assurance Trainee, Testing Program}{Paris}{FRANCE}
    {January 2013}    {
                      \begin{itemize}
                        \item Completed structured QA training program covering test methodologies and tools.
                        \item Executed functional and regression tests for web applications.
                        \item Created test cases and documented defects in issue tracking system.
                        \item Learned fundamentals of test planning, execution, and quality assurance processes.
                        \item Assisted senior QA engineers on various testing initiatives and quality reviews.
                      \end{itemize}
                    }
                    {MANUAL TESTING, JIRA, TEST PLANNING, QUALITY ASSURANCE, WEB TESTING}
  \emptySeparator
  \experience
    {January 2013}     {Digital Solutions Corp | QA Support Specialist, Testing Support}{Berlin}{GERMANY}
    {June 2011}    {
                      \begin{itemize}
                        \item Provided QA support and testing coordination for web-based business applications.
                        \item Executed test cases for functional, regression, and user acceptance testing.
                        \item Documented test results and tracked defects in project management systems.
                        \item Supported deployment testing and quality verification processes.
                        \item Participated in test planning meetings and scope definition sessions.
                      \end{itemize}
                    }
                    {MANUAL TESTING, JIRA, CONFLUENCE, WEB TESTING, UAT, QUALITY ASSURANCE}
  \emptySeparator
  \experience
    {June 2011}     {Enterprise Systems Ltd | QA Tester, Manual Testing}{Brussels}{BELGIUM}
    {January 2011}    {
                      \begin{itemize}
                        \item QA Tester for enterprise resource planning and business intelligence systems.
                        \item Executed functional and integration test cases across multiple business modules.
                        \item Reported and tracked defects using JIRA issue tracking system.
                        \item Collaborated with developers and business analysts on quality requirements.
                        \item Created and maintained test documentation and test case libraries.
                      \end{itemize}
                    }
                    {MANUAL TESTING, JIRA, ERP SYSTEMS, FUNCTIONAL TESTING, TEST DOCUMENTATION} 
  \emptySeparator   
  \experience
    {January 2011}     {Nexus Software Services | Junior QA Tester, Quality Testing}{Stockholm}{SWEDEN}
    {August 2010}    {
                      \begin{itemize}
                        \item Junior QA Tester performing manual and basic automation testing on web applications.
                        \item Execution of test scenarios and test case validation.
                        \item Identification and documentation of software defects.
                        \item Participation in test cycles and release verification activities.
                        \item Support in setting up test environments and preparing test data.
                      \end{itemize}
                    }
                    {MANUAL TESTING, WEB TESTING, JIRA, TEST EXECUTION, QUALITY ASSURANCE}
  \emptySeparator
\end{experiences}